XXXXX

### 2014-12-16 paper/RDF validation requirements/RDF validation requirements.tex
RDF validation requirements updated
cardinality shortcuts
Context-Specific Exclusive OR of Properties example

\tb{ToDo. OWL 2 DL}

@@

:CC1 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty foaf:name ;
    owl:allValuesFrom xsd:string ] .
:CC2 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty foaf:givenNme ;
    owl:allValuesFrom xsd:string ] .
\end{ex}

@@

@@

>>>>

%\tb{ToDo. OWL 2 DL}

@@

:CC1 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty foaf:name ;
    owl:allValuesFrom xsd:string ] .
:CC2 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty foaf:givenName ;
    owl:allValuesFrom xsd:string ] .
\end{ex}

@@

\begin{ex}
# ShEx
# ----
<FeelingForce> { (  
    :attackingBySword xsd:boolean | 
    :attackingByForce xsd:boolean ) }
\end{ex}

\begin{ex}
# OWL 2 DL
# --------
:FeelingForce owl:disjointUnionOf ( :CC1 :CC2 ) . 
:CC1 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty :attackingBySword ;
    owl:allValuesFrom xsd:boolean ] .
:CC2 rdfs:subClassOf [
    a owl:Restriction ;
    owl:onProperty :attackingByForce ;
    owl:allValuesFrom xsd:boolean ] .
\end{ex}

\begin{itemize}
	\item :FeelingForce $\equiv$ 1 :attackingBySword (range xsd:boolean) XOR 1 :attackingByForce (range xsd:boolean)
\end{itemize}

\begin{DL}
A $\equiv$ $\forall$ :attackingBySword . xsd:boolean \\
B $\equiv$ $\forall$ :attackingByForce . xsd:boolean \\ 
:FeelingForce $\sqsubseteq$ ($\neg$ A $\sqcap$ B) $\sqcup$ (A $\sqcap$ $\neg$ B) \\
\end{DL}

@@

\section{Cardinality Shortcuts}

\begin{itemize}
  \item In most Library applications, these tend to appear in pairs, with repeatable / non-repeatable establishing max cardinality and optional / mandatory establishing min cardinality.
	\item Optional \& Non-Repeatable = [0,1]
  \item Optional \& Repeatable = [0,*]
  \item Mandatory \& Non-Repeatable = [1,1]
  \item Mandatory \& Repatable = [1,*]
\end{itemize}

\end{document}
